%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[margin=75pt]{geometry}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-1pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Howon Kim}} & Email: \href{mailto:howonkim@berkeley.edu}{howonkim@berkeley.edu} $\cdot$ Mobile: \href{tel:+14086282000}{+1(408)-628-2000}\\
  {Software Engineer} &LinkedIn: \href{https://www.linkedin.com/in/howonkim}{howonkim} $\cdot$ Github: \href{https://github.com/howon-kim}{howon-kim}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California at Berkeley}{Berkeley, CA}
      {Bachelor of Art in Computer Science}{Aug. 2018 -- May. 2021}
    \resumeItemListStart
        \resumeItem{Coursework}{Data Structures, Artificial Intelligence, Techniques of Data Science, Software Engineering, Discrete Mathematics and Probability, Adaptive Instruction Methods in CS.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
        {Samsung Electronics}{South Korea}
        {Software Engineer Intern at Framework Department}{Jun 2020 - Aug 2020}
        \resumeItemListStart
            \resumeItem{ML-NLP}
            {EDA, lemmatize, and tokenize the notification data. Create generative statistical model using Latent Dirichlet Allocation to cluster uncategorized datas into several topics.}
            \resumeItem{Query/Android}
            {Analyze the company's  legacy framework code and research how to improve the search queries of big datas.}
            \resumeItemListEnd
            
                  \resumeSubheading
        {Altoy Games}{South Korea}
        {Software Engineer as CTO(Member of Co-founder)}{Jan 2020 - Jul 2020}
        \resumeItemListStart 
            \resumeItem{C-sharp}
            {Write scripts to control the game components to use different techniques such as coroutine, path-finding algorithm, and singleton pattern.}
            \resumeItem{Unity}
            {Familiar with Unity features in 2D and 3D  includes physics, lighting, AR, and pixel-perfect.}
            \resumeItem{Product Management}
            {Educate new software engineer and leads the project in technical aspect.}
            \resumeItem{Performance}
            {1 Million Korean Won (About 84,000 USD) Funded by Korean Government.}
            \resumeItemListEnd
            
    \resumeSubheading
        {University of California, Berkeley}{Berkeley, CA}
        {Computer Science Department Tutor}{Jan 2019 - Apr 2019}
        \resumeItemListStart
            \resumeItem{Programming and Data Structure}
            {Teach programming skills using Python and Data Structure using Java.}
            \resumeItem{Data Analysis}
            {Tutor data science; Teach how to classify big data, visualize it, and interpret it.}
            \resumeItem{Skillset}{Through Adaptive Instruction Methods in Computer Science, learn and teach how to illustrate big-idea into practice; tutor computer and data science by considering psycho-social factors that affect learning in all levels.}
            \resumeItemListEnd
      \resumeSubHeadingListEnd

    

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{RISC-V Neural Net}{Implemented Artificial Neural Net(ANN) to classify handwritten digits into actual numbers by using numerical operations such as vector inner product, matrix multiplication, and thresholding by RISC-V assembly language.}
    \resumeSubItem{Ham and Spam Detection}{Made spam detection using logistic regression model and K-fold cross validation to validate the sigmoid function.}
    \resumeSubItem{Interactive 2D Game}{Designed own data structure to save different tiles, locations of stars and characters. Made own algorithm to generate a randomized game map each time a player played.}
    \resumeSubItem{Collaborative Travel Schedule Application}
      {Developed iOS Application using Swift, Firebase, MapKit, and Core Location. Users can add or remove location pins for travel plan with the  location data synced with Firebase.}
    \resumeSubItem{Maps}
      {Wrote a library package using Java to emulate a stripped-down version of Google maps. Using Dijkstra’s algorithm and A*, the package finds the shortest route to a point from two or more locations and prints out directions and distance.}
    \resumeSubItem{Language Identification}
      {Built a Recurrent Neural Network (RNN) model that identifies language for one word at a time.}
    \resumeSubItem{Pacman AI}
      {Built pacman agents on Gridworld, then applied them to a simulated robot controller (Crawler) and Pacman using value iteration and Q-learning.}
      \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {Java, Python, C, C++, C-Sharp, SQL, Pandas, Swift, LaTeX.}
    \resumeSubItem{Technologies}
    {MySQL, Git, Unity 3D, Xcode.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
